---
title: "Cluster TEST"
author: "Dylan McGee"
date: "9/14/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## FIRST CLUSTER RUN
##import dataset/add libraries
```{r}
library(tidyverse)
library(fpc)
master_sheet <-read.csv("data/Test Run 9.csv")
```

#Create a fererence dataframe by removing all non numeric variables from main dataset into its own seperate dataset
```{r}
references <- master_sheet[1:3]
cluster_master_sheet <- master_sheet[4:14]
```


#Making Correlations
```{r}
library(corrplot)
library(gplots)

correlation <- cor(cluster_master_sheet)

corrplot(correlation, tl.col = "black")
```
#Cleaning up Correlation
```{r}
library(ggplot2)
corrplot(correlation, method = "shade", shade.col = NA, tl.col = "black") 
```
#Create K Means Cluster 
```{r}
scaled_master_sheet <-scale(cluster_master_sheet)
wss <- (nrow(scaled_master_sheet)-1)*sum(apply(scaled_master_sheet,2,var))
for (i in 2:20) wss[i] <- sum(kmeans(scaled_master_sheet,
           centers = i)$withinss)
plot(1:20, wss, type="b", xlab="Number of Clusters",
     ylab="Within groups sum of squares", main = "Elbow Plot for No. of Clusters")
```

```{r}
set.seed(500)
fit1 <- kmeans(cluster_master_sheet, 6, nstart=25)

library(cluster)
set.seed(500)
clusplot(cluster_master_sheet, fit1$cluster, color = TRUE, shade = TRUE, labels = 2, lines=0, main = "K Means Plot")
```




```{r}
library(plotly)
fig <- plot_ly(cluster_master_sheet, x= ~ K., y = ~GB., z = ~FB., color = ~fit1$cluster)
fig
```

#Creating Seperate Data Frames for each Cluster
```{r}
cluster_master_sheet <- data.frame(cluster_master_sheet, fit1$cluster)

cluster1 <- cluster_master_sheet[which(cluster_master_sheet$fit1.cluster=='1'),]
cluster2 <- cluster_master_sheet[which(cluster_master_sheet$fit1.cluster=='2'),]
cluster3 <- cluster_master_sheet[which(cluster_master_sheet$fit1.cluster=='3'),]
cluster4 <- cluster_master_sheet[which(cluster_master_sheet$fit1.cluster=='4'),]
cluster5 <- cluster_master_sheet[which(cluster_master_sheet$fit1.cluster=='5'),]
cluster6 <- cluster_master_sheet[which(cluster_master_sheet$fit1.cluster=='6'),]
```

summary(cluster1)
summary(cluster2)
summary(cluster3)
summary(cluster4)
summary(cluster5)
summary(cluster6)


#Merging Clusters with reference data
```{r}
references <- data.frame(references, fit1$cluster)

players1 <- references[which(references$fit1.cluster=='1'),]
players2 <- references[which(references$fit1.cluster=='2'),]
players3 <- references[which(references$fit1.cluster=='3'),]
players4 <- references[which(references$fit1.cluster=='4'),]
players5 <- references[which(references$fit1.cluster=='5'),]
players6 <- references[which(references$fit1.cluster=='6'),]


clusters <-rbind(players1,players2,players3,players4,players5, players6)
write.csv(clusters, file = "Clustered Results 12.csv")
```

```{r}
summary1<-summary(cluster1)
summary2<-summary(cluster2)
summary3<-summary(cluster3)
summary4<-summary(cluster4)
summary5<-summary(cluster5)
summary6<-summary(cluster6)


summaries <- rbind(summary1, summary2, summary3, summary4, summary5, summary6)

write.csv(summaries, file = "Cluster Summaries 12.csv")
```
